A Modular Framework for Developing, Deploying, and Evaluating Game-Theoretic Strategy Design Exercises

### 2018-05-08 paper.tex
Turned it in!

My primary goal, which unifies my work and sets it apart from past work on this subject, has been to discover modularity and decrease assignment-to-assignment rewriting.
As measured using \texttt{cloc}, development of the fourth strategy design exercise required only 33\% of the code be modified from previous assignments~\cite{s18}.\footnote{69 lines of code were changed out of 208 lines of code total in the development of the auctions assignment. This data also demonstrates how the assignment handouts are fairly succinct.}
As illustrated in Figure~\ref{fig:instructortime}, which shows each assignment from Spring 2018 in chronological order, instructor time usage dropped radically with each exercise, demonstrating the benefits of modular design.\footnote{This data is exaggerated by the overhead of modularization and includes time spent on framework development where that was a direct dependency of instructor work.}

\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.75\linewidth]{instructortime.png}
  \caption{Instructor time usage dropped radically as my framework was deployed. (Table~\ref{table:time})}\label{fig:instructortime}
\end{figure}

@@

Student polling data gathered at multiple points during the semester confirms that student engagement with newly released tools coincided with decreased rates of illegal submissions.
After the first two strategy design exercises, during which only the handout was provided, 68 of 74 respondents (out of 142 enrolled students) reported having used the handout to test their strategies~\cite{survey12}.
At the end of the course, students were asked to give feedback on changes in strategy design write-up grading.
As a part of that survey, students were asked: which of the resources developed as a part of this work they used in the process of developing their strategies?
Of the 142 enrolled students, there were 31 survey respondents, and 29 of the survey respondents used some of the provided infrastructure.
As shown in Figure~\ref{fig:usage2}, most students made usage of some of the additional resources.
\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.75\linewidth]{usage2.png}
  \caption{Students used the additional resources provided with Ultimatum and Auction~\cite{survey34}.}\label{fig:usage2}
\end{figure}
Individual responses show an even higher rate of usage than this data suggests: 24 of the 31 respondents used either the ``Check Submit'' button or the leaderboard to test a strategy.

Through the development of these tools, I have improved student and instructor experiences.
I verified this achievement by surveying the current students of COS 445 under the supervision of Professor Weinberg.
In addition to usage data referenced above, survey respondents also evaluated their subjective rating for how useful the provided framework was in the design of their strategies.
Initial responses shown in Figure~\ref{fig:useful1} to the fully functioning simulation software developed using my framework were positive.
This ``testing infrastructure'' was provided in the handout for the first two software design exercises.
As noted previously, even this handout provided more advanced functionality than had been available to students in previous offerings of COS 445.
\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.75\linewidth]{useful1.png}
  \caption{Students found the handout provided with Matchings and Elections useful~\cite{survey12}.}\label{fig:useful1}
\end{figure}

After the deployment of the ``Check Submit'' button and leaderboard, students had access to three different evaluation criteria for their strategies.
Figure~\ref{fig:useful2} demonstrates that students later in the semester positively evaluated all three tools, and that students had become more supportive over time of the ability to test many different strategies on their own computers.
This suggests an alternate interpretation of the decrease in illegal submissions: not just is it important to provide quality tooling to students, but also it is important for the students to use those tools.
\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.75\linewidth]{useful2.png}
  \caption{Students found the additional resources provided with Ultimatum and Auction useful~\cite{survey34}.}\label{fig:useful2}
\end{figure}

@@

Professor Weinberg: We have \textbf{significantly} improved instructor involvement. I didn't actually touch any of the software directly, so I don't know how to comment on that. But I felt like the challenges mostly ran themselves. We talked briefly to set it up. We talked briefly to decide how to grade, and I didn't have to answer any technical questions for students in between.
\end{displayquote}
My own experience an undergraduate course assistant using the framework I have developed in this work corroborates this claim: this project has led to better course experiences for all involved.

>>>>

My primary goal, which unifies my work and sets it apart from past work on this subject, has been to discover modularity and decrease assignment-to-assignment rewriting.
As measured using \texttt{cloc}, development of the fourth strategy design exercise required only 33\% of the code be modified from previous assignments~\cite{s18}.\footnote{69 lines of code were changed out of 208 lines of code total in the development of the auctions assignment. This data also demonstrates how the assignment handouts are fairly succinct.}
As illustrated in Figure~\ref{fig:instructortime}, which shows each assignment from Spring 2018 in chronological order, instructor time spent building and grading assignments dropped radically with each exercise, demonstrating the benefits of modular design.\footnote{This data is exaggerated by the overhead of modularization and includes time spent on framework development where that was a direct dependency of instructor work.}
Improving the efficiency of the assignment design process was not within the scope of this work.
\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.75\linewidth]{instructortime.png}
  \caption{Instructor time usage dropped radically as my framework was deployed (Table~\ref{table:time}).}\label{fig:instructortime}
\end{figure}

@@

Student polling data gathered at multiple points during the semester confirms that student engagement with newly released tools coincided with decreased rates of illegal submissions.
The first poll was taken after the first two strategy design exercises, during which only the handout was provided.
Out of 142 enrolled students, there were 74 survey responses, of which 68 reported having used the handout to test their strategies~\cite{survey12}.
At the end of the course, students were asked to give feedback on changes in strategy design write-up grading.
As a part of that survey, students were asked which of the resources developed as a part of this work they used in the process of developing their strategies.
There were 31 responses to the second survey and 29 of these reported use of some of the provided infrastructure.
As shown in Figure~\ref{fig:usage2}, most students made usage of some of the additional resources.
\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.75\linewidth]{usage2.png}
  \caption{Students used the additional resources provided with Ultimatum and Auction~\cite{survey34}.}\label{fig:usage2}
  \caption*{Percentages include only students who reported using any provided resource.}
\end{figure}
Individual responses show an even higher rate of usage than this data suggests: 24 of the 31 respondents used either the ``Check Submit'' button or the leaderboard to test a strategy.

Through the development of these tools, I have improved student and instructor experiences.
I verified this achievement by surveying the current students of COS 445 under the supervision of Professor Weinberg.
In addition to usage data referenced above, survey respondents also evaluated their subjective rating for how useful the provided framework was in the design of their strategies.
Initial responses shown in Figure~\ref{fig:useful1} to the fully functioning simulation software developed using my framework were positive.
This ``testing infrastructure'' was provided in the handout for the first two software design exercises.
As noted previously, even this handout provided more advanced functionality than had been available to students in previous offerings of COS 445.
\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.75\linewidth]{useful1.png}
  \caption{Students found the handout provided with Matchings and Elections useful~\cite{survey12}.}\label{fig:useful1}
  \caption*{Scores were given from 1 (not useful) to 5 (useful).}
\end{figure}

After the deployment of the ``Check Submit'' button and leaderboard, students had access to three different evaluation criteria for their strategies.
Figure~\ref{fig:useful2} demonstrates that students later in the semester positively evaluated all three tools, and that students had become more supportive over time of the ability to test many different strategies on their own computers.
This suggests an alternate interpretation of the decrease in illegal submissions: it is not just important to provide quality tooling to students, but also important that the students use those tools.
\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.75\linewidth]{useful2.png}
  \caption{Students found the additional resources provided with Ultimatum and Auction useful~\cite{survey34}.}\label{fig:useful2}
\end{figure}

@@

Professor Weinberg: We have \textbf{significantly} improved instructor involvement.
I didn't actually touch any of the software directly, so I don't know how to comment on that.
But I felt like the challenges mostly ran themselves.
We talked briefly to set it up.
We talked briefly to decide how to grade, and I didn't have to answer any technical questions for students in between.
\end{displayquote}
My own experience an undergraduate course assistant using the framework I have developed in this work corroborates the claim that this project has led to better course experiences for all involved.
